Predictors of frog survival following translocations - create dataset

### 2022-03-06 code/translocation_survival_createdata.Rmd
Edit code to access cmr-analysis files locally

The files accessed by this code chunk are generated by code in the xxxxx_createdata_mrmr.Rmd files in the [cmr-analysis](https://github.com/SNARL1/cmr-analysis) GitHub repo.
To avoid copying those files to this project and duplicating files as a result, this code chunk accesses those files directly.
As such, the file path used will likely need to be changed to reflect local directory structure.

```{r retrieve-translocated-frogs-data }
files <- fs::dir_ls("../../cmr-analysis/data/clean", glob = "*translocation.csv")
frog_translocation <- read_csv(files, id = "path") %>% 
  mutate(site_id = str_extract(path, "(\\d)+"), .after = path) %>%  # extracts numeric string from file path
  filter(release_date < "2021-01-01") %>% 
  rename(pit_tag_ref = pit_tag_id) %>% 
  select(-path)
rm(files)
```

@@

The files accessed by this code chunk are generated by code in the xxxxx_analysis_mrmr.Rmd files in the [cmr-analysis](https://github.com/SNARL1/cmr-analysis) GitHub repo.
To avoid copying those files to this project and duplicating files as a result, this code chunk accesses those files directly.
As such, the file path used will likely need to be changed to reflect local directory structure.

```{r retrieve-frog-survival-data}
files <- fs::dir_ls("../../cmr-analysis/out/tables", glob = "*ind.csv")
frog_survival <- read_csv(files, id = "path") %>% 
  mutate(site_id = str_extract(path, "(\\d)+"), .after = path) %>%  # extracts numeric string from file path
  rename(years_since_intro = years_since_introduction,
         pit_tag_ref = pit_tag_id) %>% 
  filter(years_since_intro == 1) %>% 
  select(site_id, release_date, years_since_intro, pit_tag_ref, median_survival)
rm(files)
```

>>>>

The files accessed by this code chunk are generated by code in the xxxxx_createdata_mrmr.Rmd files in the [cmr-analysis](https://github.com/SNARL1/cmr-analysis) GitHub repo (version 2021).

```{r retrieve-translocated-frogs-data }
files <- fs::dir_ls("../data/raw/cmr-analysis/translocation")  
frog_translocation <- read_csv(files, id = "path") %>% 
  mutate(site_id = str_extract(path, "(\\d)+"), .after = path) %>%  # extracts numeric string from file path
  filter(release_date < "2021-01-01") %>% 
  rename(pit_tag_ref = pit_tag_id) %>% 
  select(-path)
rm(files)
```

@@

The files accessed by this code chunk are generated by code in the xxxxx_analysis_mrmr.Rmd files in the [cmr-analysis](https://github.com/SNARL1/cmr-analysis) GitHub repo (version 2021).

```{r retrieve-frog-survival-data}
files <- fs::dir_ls("../data/raw/cmr-analysis/survival")
frog_survival <- read_csv(files, id = "path") %>% 
  mutate(site_id = str_extract(path, "(\\d)+"), .after = path) %>%  # extracts numeric string from file path
  rename(years_since_intro = years_since_introduction,
         pit_tag_ref = pit_tag_id) %>% 
  filter(years_since_intro == 1) %>% 
  select(site_id, release_date, years_since_intro, pit_tag_ref, median_survival)
rm(files)
```
